

%%% Choose a language %%%

\newif\ifEN
\ENtrue   % uncomment this for english
%\ENfalse   % uncomment this for czech

%%% Configuration of the title page %%%

\def\ThesisTitleStyle{mff} % MFF style
%\def\ThesisTitleStyle{cuni} % uncomment for old-style with cuni.cz logo
%\def\ThesisTitleStyle{natur} % uncomment for nature faculty logo

\def\UKFaculty{Faculty of Mathematics and Physics}
%\def\UKFaculty{Faculty of Science}

\def\UKName{Charles University in Prague} % this is not used in the "mff" style

% Thesis type names, as used in several places in the title
%\def\ThesisTypeTitle{\ifEN BACHELOR THESIS \else BAKALÁŘSKÁ PRÁCE \fi}
\def\ThesisTypeTitle{\ifEN MASTER THESIS \else DIPLOMOVÁ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN RIGOROUS THESIS \else RIGORÓZNÍ PRÁCE \fi}
%\def\ThesisTypeTitle{\ifEN DOCTORAL THESIS \else DISERTAČNÍ PRÁCE \fi}
%\def\ThesisGenitive{\ifEN bachelor \else bakalářské \fi}
\def\ThesisGenitive{\ifEN master \else diplomové \fi}
%\def\ThesisGenitive{\ifEN rigorous \else rigorózní \fi}
%\def\ThesisGenitive{\ifEN doctoral \else disertační \fi}
%\def\ThesisAccusative{\ifEN bachelor \else bakalářskou \fi}
\def\ThesisAccusative{\ifEN master \else diplomovou \fi}
%\def\ThesisAccusative{\ifEN rigorous \else rigorózní \fi}
%\def\ThesisAccusative{\ifEN doctoral \else disertační \fi}



%%% Fill in your details %%%

% (Note: \xxx is a "ToDo label" which makes the unfilled visible. Remove it.)
\def\ThesisTitle{Asynchronous Duet Benchmarking}
\def\ThesisAuthor{Tomáš Drozdík}
\def\YearSubmitted{2023}

% department assigned to the thesis
\def\Department{Department of Distributed and Dependable Systems}
% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Department}

\def\Supervisor{Mgr. Vojtěch Horký, Ph.D.}
\def\SupervisorsDepartment{Department of Distributed and Dependable Systems}

% Study programme and specialization
\def\StudyProgramme{Software Systems}
\def\StudyBranch{System programming}

\def\Dedication{%
I want to thank my supervisor, family and friends for their patience and support.
}

\def\AbstractEN{%
% Abstracts are an abstract form of art. Use the most precise, shortest sentences that state what problem the thesis addresses, how it is approached, pinpoint the exact result achieved, and describe the applications and significance of the results. Highlight anything novel that was discovered or improved by the thesis. Maximum length is 200 words, but try to fit into 120. Abstracts are often used for deciding if a reviewer will be suitable for the thesis; a well-written abstract thus increases the probability of getting a reviewer who will like the thesis.
Accurate regression detection in volatile environments such as the public cloud is difficult.
Cloud offers an accessible and scalable infrastructure to run benchmarks, but the traditional benchmarking methods often fail to predict regressions reliably.
Duet method acknowledges the variability and runs the workloads in parallel, assuming similar outside impact symmetry.
This thesis examines a duet variant that does not synchronize harness iterations which enables broader use of this method.
The asynchronous duet method can detect $1-5\%$ slowdowns for most of the tested benchmarks in volatile environments while reducing the overall costs by up to $50\%$.
Measurements were obtained by a benchmark automation tool for running and processing benchmarks from multiple suites.
This tool can run benchmarks with sequential and both duet methods utilizing containers for portability.
}


\def\AbstractCS{
Přesná detekce zpomalení benchmarků v nestabilních prostředích, jako je veřejný cloud, je obtížná.
Cloud nabízí dostupnou a škálovatelnou infrastrukturu pro spouštění benchmarků, ale tradiční metody benchmarkingu často nezvládají spolehlivě rozpoznat zpomalení.
Metoda duet bere variabilitu na vědomí a běží benchmarky paralelně za předpokladu podobné vnější symetrie dopadu.
Tato práce zkoumá variantu metody duet, která nesynchronizuje iterace, což umožňuje širší využití této metody.
Metoda asynchronního duetu dokáže detekovat zpomalení v rozsahu $1 - 5\%$ u většiny testovaných benchmarků ve volatilních prostředích a zároveň snižuje celkové náklady až o $50\%$.
Měření byla získána nástrojem pro automatizované spouštění a zpracování benchmarků z více sad.
Tento nástroj může spouštět jak sekvenční metodu tak obě duet metody využívající kontejnery pro přenositelnost.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces.
% Keywords are useful for indexing and searching for the theses by topic.
\def\Keywords{%
{benchmarking} {cloud} {duet} {containers}
}

% If your abstracts are long and do not fit in the infopage, you can make the
% fonts a bit smaller by this setting. (Also, you should try to compress your abstract more.)
% Alternatively, consider increasing the size of the page by uncommenting the
% geometry modification in thesis.tex.
\def\InfoPageFont{}
%\def\InfoPageFont{\small}  %uncomment to decrease font size

\ifEN\relax\else
% If you are writing a czech thesis, you additionally need to fill in the
% english translation of the metadata here!
\def\ThesisTitleEN{\xxx{Thesis title in English}}
\def\DepartmentEN{\xxx{Name of the department in English}}
\def\DeptTypeEN{\xxx{Department}}
\def\SupervisorsDepartmentEN{\xxx{Superdepartment}}
\def\StudyProgrammeEN{\xxx{study programme}}
\def\StudyBranchEN{\xxx{study branch}}
\def\KeywordsEN{%
\xxx{{key} {words}}
}
\fi
